---
title: "Colautti 812-week1 refresher"
author: "HT"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("ggplot2")
```


```{r setup, include=FALSE}
source("http://bit.ly/theme_pub") # what does this hold? - bottom of rmd
```

#Random numbers#

Generate a vector of 100 numbers drawn from a random normal dist with mean 10, sd 5

```{r}
v <- rnorm(100, 10, 5)
```
Same, but from Pois, rate = 15
```{r}
v_pois <- rpois(100, 15)
```

Fun fact, random numbers generated by a computer are generated by a calculation from a ‘seed’ number, so they are never truly random. They act random because the seed number is typically something like the millionth of a second of the time on your computer’s internal clock.

It’s not just philosophical, it is also useful for testing and debugging since you can set the seed to generate the same ‘random’ numbers.

```{r}
xx <- seq(0,30, length=200)
qplot(xx, pnorm(xx, 10, 5))
```

#sampling functions: `sample` vs `rep` vs `replicate` vs `seq`

```{r}
sample(c("A", "B", "C"), 10, replace=T)
rep(rnorm(3), 3)
replicate(3, rnorm(3), simplify = "array")
```

#objects: `element` vs `vector` vs `matrix` vs `dataframe`

```{r}
list(name="mylist", numbers=rnorm(10), letters=sample(c("A", "B", "C"), 10, replace = T))
```
# `print` vs `paste`

paste makes a vector of strings

```{r}
print(v_pois)
paste(v_pois)

#string will let you do this:
#paste can do this, but print can't
print(v_pois, "num")
paste(v_pois, "num")

#also possible here:
paste(v_pois, collapse = ",")
```

```{r}
XDat <- data.frame(x=rnorm(100), y=rnorm(100))
ggplot(aes(x=x), data=XDat) + geom_histogram() + theme_pub()
ggplot(aes(x=x, y=y), data=XDat) + geom_point() + theme_pub()

plot(XDat$x, XDat$y)
```
#dplyr things
`%>%`
`join` - left, right, inner and outer
`pivot` - wider, longer

#functions
example - theme_pub

#flow control - for and if statements
```{r}
if(1==1){
print("True")
}else {
  print("False")
}

ifelse(1==1, "T", "F")
```  

```{r}
#source("http://bit.ly/theme_pub")
theme_pub <- function (base_size = 12, base_family = "") {
  theme_classic(base_size = base_size, base_family = base_family) %+replace% 
    theme(
      axis.text = element_text(colour = "black"),
      axis.title.x = element_text(size=16, margin=margin(t=5)),
      axis.text.x = element_text(size=10),
      axis.title.y = element_text(size=16,angle=90, margin=margin(r=5)),
      axis.text.y = element_text(size=10),
      axis.ticks = element_blank(), 
      panel.background = element_rect(fill="white"),
      panel.border = element_blank(),
      plot.title=element_text(face="bold", size=20),
      legend.position="none"
    ) 
}

getwd()
#setting relative path to theme_pub in scripts
```

#git instructions:
A repository, sometimes shortened to just repo, is just a place to store your code. GitHub is a website that makes it easy to create and manage a repository. It uses a tool called git, which we can use to interface with GitHub and R Studio.

Git and GitHub are useful for sharing code and collaborating on projects, which you'll do later in the course. But you can also think of GitHub as an online CV or Resume, which you can use to showcase your coding contributions. 

<https://www.rstudio.com/resources/webinars/managing-part-2-github-and-rstudio/>
This video explains how to interface with GitHub using R Studio. It's about 45 minutes long but you can watch it at 1.25x or 1.5x to reduce the time. Watching the video will help you avoid errors when using GitHub following the instructions below.

Part I: Set up your GitHub account

Make a (free) account on GitHub.
Sign up at Github.com
You will need to choose a user name
Add a headshot and fill out other details of your profile. This will help your account stand out for the crowd, and make it easier for recruiters to get to know you. 

<https://support.posit.co/hc/en-us/articles/200532077-Version-Control-with-Git-and-SVN>
Read Version Control with Git and follow the instructions to install Git and get it set up with R Studio
NOTE: This includes instructions for two programs: Git and Subversion. 
You DO NOT need to install Subversion, only Git.

Confirm and locate Git
(Windows): Search for 'Command Prompt' from your Start Menu and type: where git
(Mac OS & Linux): Open the 'Terminal' window and type: which git
Take note of the file location that it shows after you hit 'enter'
Find where Git is installed on your computer:
Open R Studio and set up Git
Select: Tools-->Global Options-->Git/SVN
Make sure Enable version control is checked at the top
In Git Executable use the Browse button to locate the file that was output in Step 3
Part II: Create a new R project/repository

Create a new project folder:
In R Studio select File-->New Project. 
Select Version Control and then Git.
Open a Web Browser and make a new GitHub Repository
Go to your Github site (e.g. github.com/your_user_name)
Click Repositories near the top of the screen
Click the green button that says New
Give your repository a meaningful name, like BIOL432_Assignment1
Give a short description
Choose Public
Do not add a README file or select a file for .gitignore.
You may select a license if you would like to protect your code. You should do this when writing original code, but you don't have to do it for the assignments.
Click Create repository
Copy the full web address for your repository (e.g., https://github.com/your_user_name/BIOL432_Assignment1)
Link your GitHub Repo to R Studio
Return to R Studio
In the Repository URL box, paste the GitHub repository website that you just copied above, and add .git to the end. This is important -- the .git file is the file that contains the information for using Git to sync files between R Studio and GitHub.
The Project directory name box is the name of the directory on your computer that will hold all of the files that are synced with your GitHub repository. Usually, this will be the name of your project folder and it will have the same name as your GitHub repository (e.g. BIOL432_Assignment1)
Click Create Project

Examine the Git tab in R Studio
The Git Tab is usually in the top-right window of R Studio, in the same window as Environment and History.
When you start, this tab will be empty.
As you make changes to your R Project folder, you will see files appear in the git tab. 
There are three main buttons at the top of the Git tab that you should know:
Commit -- use this to commit the changes you make. Commits are like pressing 'save' on your computer, except that each commit gets a unique code, which makes it possible for you to roll back to previous commits.
Pull -- use this to pull the latest files and commits from GitHub. Go ahead a press it now. (You may be prompted to confirm your password). It's generally good practice to pull changes every time you work on a project, to make sure you are working with the latest version.
Push -- use this to push your commits to GitHub. It's generally a good idea to do this when you are done working on the project for a while. This will allow your collaborators to pull your changes from GitHub before they start working on their piece.
