---
title: "Report - Trial repository"
author: "HT"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

*Step 1 - Data generation*

Script content:
Generating data frame of 4 variables of length 100 - species, limb width, limb length and observer.

v1 - Sample with replace=T from a list of 5 species;
v2 - rnorm m=3, sd=0.8;
v3 - rnorm m=10, sd=2;
v4 - Sample with replace=T from a list of 3 observers;

```{r}
source(file = "/Users/ht/0/Stats/2 Colautti_812/trial_repo/scripts/1DataGenerato.R")
```

*Step 2 - Volume estimation*

Script content:

Formula used - 

vol of cylinder (limb) = area of surface circle*length

vol                    = pi*r^2*l

vol                    = pi*(w/2)^2*l

#check for indexing errors in read.csv - if loop to delete extra col of indexing

'measurements' overwritten to include volume column

```{r}
source(file = "/Users/ht/0/Stats/2 Colautti_812/trial_repo/scripts/2VolumeEstimato.R")
```

*Step 3 - Data summaries*

Rearrange data by species, observer and volume;
Summarize means and std devs for diff species, counts for each observer

```{r}
source(file = "/Users/ht/0/Stats/2 Colautti_812/trial_repo/scripts/3Summary.R")
```

*Step 4 - Visualization*

Script 0 content: theme from <http://bit.ly/theme_pub> for ggplot to use

Script 1 content: boxplot by species

Script 2 content: histograms(freq=T) for each species

```{r}
source(file = "/Users/ht/0/Stats/2 Colautti_812/trial_repo/scripts/theme_pub.R")
source(file = "/Users/ht/0/Stats/2 Colautti_812/trial_repo/scripts/4Visualization_1.R")
```

```{r}
source(file = "/Users/ht/0/Stats/2 Colautti_812/trial_repo/scripts/4Visualization_2.R")
```