---
title: "Report - Trial repository"
author: "HT"
date: "2023-01-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

*Step 1 - Data generation*
Script content:
Generating data frame of 4 variables of length 100 - species, limb width, limb length and observer.
v1 - Sample with replace=T from a list of 5 species
v2 - rnorm m=3, sd=0.8
v3 - rnorm m=10, sd=2
v4 - Sample with replace=T from a list of 3 observers

```{r}
source(file = "scripts/1DataGenerato.R")
```

*Step 2 - Volume estimation*
Script content:
#check for indexing errors in read.csv - if loop to delete extra row of indexing
Formula used - 
vol of cylinder (limb) = area of surface circle*length
                       = pi*r^2*l
                       = pi*(w/2)^2*l

'measurements' overwritten to include volume column

```{r}
source(file = "scripts/2VolumeEstimato.R")
```

*Step 3 - Data summaries, visualization*
Script 1 content: theme from <http://bit.ly/theme_pub> for ggplot to use
Script 2 content:
Rearrange data by species, observer and volume
Summarize means and std devs for diff species, counts for each observer
Plots - boxplot by species, histograms(freq=T) for each species

```{r}
source(file = "scripts/theme_pub.R")
source(file = "scripts/3Summary&Visualization.R")
```

